\papertitle

### 2025-01-23 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{acknowledgements}
We thank Richard Gowers for the insightful discussion that started us down this rabbit hole and for helpful comments on the manuscript.
We also thank Neil L. Allan for helpful discussions that lead to this work. 
H.R. acknowledges the Engineering and Physical Sciences Research Council for funding. 
BP plc is thanked for the financial support of J.D
through an industrial CASE (ICASE) studentship in partnership
with the Engineering and Physical Sciences Research Council. 
ICASE grant reference EP/T51763X/1.
\end{acknowledgements}

>>>>

\begin{acknowledgements}
We thank Richard Gowers for the insightful discussion that started us down this rabbit hole and for helpful comments on the manuscript.
We also thank Neil L. Allan for helpful discussions that lead to this work. 
H.R. acknowledges the Engineering and Physical Sciences Research Council for DTP funding (EP/W524414/1). 
BP plc is thanked for the financial support of J.D
through an industrial CASE (ICASE) studentship in partnership
with the Engineering and Physical Sciences Research Council (EP/T51763X/1).
\end{acknowledgements}
